---
title: "Old-style knitr chunk options are not supported"
description: "A code block declared knitr-style options in its header instead of Quarto's `#| key: value` body syntax."
code: Q-2-36
subsystem: markdown
status: stub
since: "99.9.9"
categories:
  - markdown
---

# `Q-2-36` — Old-style knitr chunk options are not supported

> Quarto Markdown does not support knitr-style chunk options in the
> header. Move options into the body using `#| key: value` syntax, or
> use the Pandoc class form `{.r ...}` instead of `{r ...}`.

## What this means

An executable code block declared its options inside the header
braces, knitr-style:

````markdown
```{r, echo=FALSE}
1 + 1
```
````

Quarto Markdown reads chunk options from the *body* of the block, not
the header. Header forms that R Markdown accepted — a bare label
(`{r test}`), a comma after the language (`{r, echo=FALSE}`), or
space-separated `key=value` pairs (`{r echo=FALSE}`) — are all
rejected with this error.

## Why this happens

- **Documents ported from R Markdown / older Quarto.** knitr chunk
  headers like `{r label, echo=FALSE, fig.width=7}` were the standard
  way to set options there.
- **Muscle memory.** Even in new documents, the knitr header form is
  easy to reach for.

## How to fix

Move each option into the body of the block using `#| key: value`
syntax:

````markdown
```{r}
#| echo: false
1 + 1
```
````

Chunk labels become `#| label:`:

````markdown
```{r}
#| label: test
1 + 1
```
````

If you only wanted a Pandoc class on a non-executable block — not
chunk options — write the language with a leading dot:

````markdown
```{.r}
1 + 1
```
````

## Related errors

- [`Q-2-8`](Q-2-8.qmd) — the retired warning code this error replaced.
