---
title: Computations
---

## Overview

A Quarto document can contain **executable cells**: fenced code blocks whose
info string is a language name wrapped in braces. Quarto hands each cell to
an [engine](engines.qmd), runs it, and splices the results into the rendered
document. For example, a cell written like this:

````markdown
```{r}
sum(1:10)
```
````

would, if run, produce `55` underneath it in the rendered page. (This page
only *shows* cells like this one — see the next section — so nothing on it
actually runs.)

## Displaying code cells without running them

Writing *about* Quarto means showing readers what a cell looks like without
running it — for example, in a tutorial or in this documentation. The rule is
the ordinary Markdown one: **a fenced code block is displayed verbatim**, so a
cell written inside one is shown, not executed.

To display the cell above instead of running it, wrap it in a fence with
*more backticks* than the cell uses:

`````markdown
````markdown
```{r}
sum(1:10)
```
````
`````

which renders as:

````markdown
```{r}
sum(1:10)
```
````

The braces stay single. Nothing about the inner cell changes — it is shown
exactly as an author would type it, which is the point: a reader can copy it
straight into their own document.

### The outer fence must be longer

Markdown decides where a fenced code block ends by matching the length of its
opening fence. So the wrapping fence only needs to be *longer* than the
longest run of backticks inside it — one backtick longer is enough. A cell
written with the ordinary three backticks is displayed by wrapping it in four;
if the content being displayed already contains a four-backtick fence, wrap
that in five, and so on.

### Cell options are displayed too

Options on the fence header, and Quarto's `#|` comment options, are part of
the cell and are displayed along with it — nothing needs to be stripped or
adjusted. A fence-header option:

````markdown
```{r, echo=FALSE}
plot(1:10)
```
````

and a `#|` comment option:

````markdown
```{r}
#| echo: false
#| label: fig-example
plot(1:10)
```
````

### Displaying a block that itself displays a cell

The same rule applies at any depth: each layer's fence just needs to be
longer than the longest fence nested inside it. To show a document like this
page — one that itself displays a cell — add one more layer of backticks:

``````markdown
`````markdown
````markdown
```{python}
1 + 1
```
````
`````
``````

::: callout-note
## Migrating from Quarto 1

Quarto 1 used doubled curly braces for this — a cell written as
`{{python}}` was displayed, with single braces, instead of running.
Quarto 2 does not support this escape: doubled braces in a fence
header produce a warning ([`Q-2-50`](../../errors/markdown/Q-2-50.qmd)),
and the fix is the `markdown` code block shown above. Dropping the
escape also means code blocks that genuinely contain doubled braces —
Jinja or Mustache templates, GitHub Actions expressions — render
correctly, where Quarto 1 would collapse them.
:::
