---
title: Computations
---

## Overview

A Quarto document can contain **executable cells**: fenced code blocks whose
info string is a language name wrapped in braces. Quarto hands each cell to
an [engine](engines.qmd), runs it, and splices the results into the rendered
document. For example, a cell written like this:

````markdown
```{r}
sum(1:10)
```
````

would, if run, produce `55` underneath it in the rendered page. (This page
only *shows* cells like this one — see the next section — so nothing on it
actually runs.)

## Displaying code cells without running them

Writing *about* Quarto means showing readers what a cell looks like without
running it — for example, in a tutorial or in this documentation. The rule is
the ordinary Markdown one: **a fenced code block is displayed verbatim**, so a
cell written inside one is shown, not executed.

To display the cell above instead of running it, wrap it in a fence with
*more backticks* than the cell uses:

`````markdown
````markdown
```{r}
sum(1:10)
```
````
`````

which renders as:

````markdown
```{r}
sum(1:10)
```
````

The braces stay single. Nothing about the inner cell changes — it is shown
exactly as an author would type it, which is the point: a reader can copy it
straight into their own document.

### The outer fence must be longer

Markdown decides where a fenced code block ends by matching the length of its
opening fence. So the wrapping fence only needs to be *longer* than the
longest run of backticks inside it — one backtick longer is enough. A cell
written with the ordinary three backticks is displayed by wrapping it in four;
if the content being displayed already contains a four-backtick fence, wrap
that in five, and so on.

### Cell options are displayed too

Options on the fence header, and Quarto's `#|` comment options, are part of
the cell and are displayed along with it — nothing needs to be stripped or
adjusted. A fence-header option:

````markdown
```{r, echo=FALSE}
plot(1:10)
```
````

and a `#|` comment option:

````markdown
```{r}
#| echo: false
#| label: fig-example
plot(1:10)
```
````

### Displaying a block that itself displays a cell

The same rule applies at any depth: each layer's fence just needs to be
longer than the longest fence nested inside it. To show a document like this
page — one that itself displays a cell — add one more layer of backticks:

``````markdown
`````markdown
````markdown
```{python}
1 + 1
```
````
`````
``````

::: callout-note
## Migrating from Quarto 1

Quarto 1 used doubled curly braces for this — a cell written as
`{{python}}` was displayed, with single braces, instead of running.
Quarto 2 does not support this escape: doubled braces in a fence
header produce a warning ([`Q-2-50`](../../errors/markdown/Q-2-50.qmd)),
and the fix is the `markdown` code block shown above. Dropping the
escape also means code blocks that genuinely contain doubled braces —
Jinja or Mustache templates, GitHub Actions expressions — render
correctly, where Quarto 1 would collapse them.
:::

## Inline expressions

A document can also compute a value **inline** --- inside a sentence, or
inside an attribute --- so that the result appears in place of the
expression. Quarto has two spellings for this, and they differ in how the
computed value is inserted.

The **brace spelling** mirrors the cell syntax and works across engines:

````markdown
The current release is `{r} release_version`.
````

The **classic spelling** is knitr's own, inherited from R Markdown, and
predates Quarto. It is available with the knitr engine only:

````markdown
The current release is `r release_version`.
````

### The two spellings insert the value differently

The brace spelling **escapes** Markdown's special characters in the value:
whatever the expression returns is shown as text, exactly as it came out. The
classic spelling inserts the value **as Markdown**, so formatting carried in
the value is interpreted.

With `notice` set to `**important**`:

| Written              | Renders as      |
|----------------------|-----------------|
| `` `{r} notice` ``   | `**important**` |
| `` `r notice` ``     | **important**   |

To opt the brace spelling into Markdown, wrap the value in knitr's `I()`:

````markdown
The notice is `{r} I(notice)`.
````

That makes the two spellings equivalent: `` `r x` `` does the same thing as
`` `{r} I(x)` ``.

Reach for the brace spelling when the value comes from somewhere you do not
control. Markdown admits inline HTML, so a value inserted as Markdown can
bring markup with it; the brace spelling's escaping is the default for
exactly that reason.

### Where inline expressions work

In prose, and in attribute values --- a fenced div's attributes, or a link
title:

````markdown
The current release is `{r} release_version`.

::: {#hero data-version="`{r} release_version`"}
Download the latest build.
:::

[Download](https://example.com/dl "Version `{r} release_version`")
````

### Writing about an inline expression

The rule is the one from [Displaying code cells without running
them](#displaying-code-cells-without-running-them), and nothing about it
changes for inline expressions: write it inside a `markdown` block and it is
displayed rather than run.

````markdown
```markdown
The current release is `{r} release_version`.
```
````

which renders as:

```markdown
The current release is `{r} release_version`.
```

The expression is shown exactly as an author would type it, together with the
prose around it, so a reader can copy the whole line into their own document.
As with cells, the wrapping fence only needs to be longer than the longest run
of backticks inside it.

The block has to be a `markdown` block, or a fence carrying no language at
all. A fence labelled with some other language --- ```` ```r ````, say ---
displays its text but does not stop an expression inside it from running, so
reach for `markdown` when what you are showing is Quarto syntax.

::: callout-note
## Migrating from Quarto 1

Quarto 1 had a doubled-brace escape for inline expressions too: `` `{{r}} x` ``
was displayed as `` `{r} x` ``. Quarto 2 drops it for the same reason it drops
the doubled-brace escape for cells --- the `markdown` code block above does the
job, and leaving doubled braces alone is what lets Jinja and Mustache templates
render correctly.
:::
