# Q-2-36 cases: knitr-style headers (rejected) vs. Pandoc-style headers (accepted)

Sections (1)–(7) are knitr-style chunk headers — `{lang ...}` with no
leading `.` on the language — that should fire Q-2-36. Section (8) is
the Pandoc-style class form `{.lang ...}` that must stay valid; included
as a negative control so the discrimination is exercised in fixtures.

The block body is the same `1+1` everywhere so any non-header error is
easy to spot.

## (1) Bare label (reporter's case)

```{r test}
1+1
```

## (2) Space + key=value (single arg, R)

```{r echo=FALSE}
1+1
```

## (3) Space + key=value (quoted, R)

```{r label="foo"}
1+1
```

## (4) Comma + space + key=value (canonical knitr, R)

```{r, label="foo", echo=FALSE}
1+1
```

## (5) Space + key=value (Python)

```{python echo=FALSE}
1+1
```

## (6) Space + key=value (Julia)

```{julia label="foo"}
1+1
```

## (7) Mixed: old header + new #| option (per scope decision, must still error)

```{r echo=FALSE}
#| label: mixed
1+1
```

## (8) Pandoc class form — MUST stay valid (negative control)

```{.r echo=FALSE}
1+1
```
